### 2017-11-14 ident/docs/ident_manuscript.tex
add stements about project in intro

\begin{document}
	\section{Introduction:}
	\paragraph{Outline:}
	\begin{itemize}
		\item How dynamic models of metabolism are defined in biology
		\item How parameter values is important for model-based prediction and design of metabolism
		\item importance of parameter identifiability, structural and practical identifiability for dynamic models of metabolism
		\item work done in the are of structural identifiability (numerical and symbolic/computer algebra methods) - local vs global identifiability
		\item work done in the area of practical identifiability (numerical and symbolic/computer algebra methods)
		\item work done in this paper for practical identifiability
		\item scalability of computer algebra-based methods for structural identifiability (using CRNT to reduce networks to make structural identifiability scalable)
	\end{itemize}
	\subsection{Identifiability analysis: Definitions and Formulations}
	Any nonlinear dynamical system can be represented by a set of states $\mathbf{x}$, observables $\mathbf{y}$ that are dependent on the states, parameters $\mathbf{\mu}$, and inputs $u$ as in Equation (\ref{eq:dynmodel}). 
	\begin{subequations}\label{eq:dynmodel}
		\begin{align}
		\dot{\mathbf{x}} = g(\mathbf{x},\mathbf{\mu},u)\\
		\mathbf{y} = h(\mathbf{x},\mathbf{\mu},u)
		\end{align}
	\end{subequations}
	Identifiability concerns with the ability to determine a unique solution to the problem of estimating parameters $\mathbf{\mu}$ from given data on the system observables $\mathbf{y}$ for inputs $u$ \parencite{McLean2012}.	The identifiability of parameters in nonlinear models of physical processes can be classified into two categories: structural and practical identifiability.

>>>>

\begin{document}
	\section{Introduction:}
	\paragraph{Outline:}
	\begin{itemize}
		\item How dynamic models of metabolism are defined in biology
		\item How parameter values is important for model-based prediction and design of metabolism
		\item importance of parameter identifiability, structural and practical identifiability for dynamic models of metabolism
		\item work done in the are of structural identifiability (numerical and symbolic/computer algebra methods) - local vs global identifiability
		\item work done in the area of practical identifiability (numerical and symbolic/computer algebra methods)
		\item work done in this paper for practical identifiability
		Here, we present a computer algebra-based method to establish practical identifiability of kinetic models of metabolic networks. Our method establishes posterior identifiability for each individual flux separately and can potentially be scaled-up to models of large metabolic networks. To illustrate this point, we have demonstrated the application of our methodology for the kinetic model of the red blood cell hepatocyte metabolic network.
		\item scalability of computer algebra-based methods for structural identifiability (using CRNT to reduce networks to make structural identifiability scalable) (move to discussion - may be)
	\end{itemize}
	\subsection{Identifiability analysis: Definitions and Formulations}
	Any nonlinear dynamical system can be represented by a set of states $\mathbf{x}$, observables $\mathbf{y}$ that are dependent on the states, parameters $\mathbf{\mu}$, and inputs $u$ as in Equation (\ref{eq:dynmodel}). 
	\begin{subequations}\label{eq:dynmodel}
		\begin{align}
		\dot{\mathbf{x}} = g(\mathbf{x},\mathbf{\mu},u)\\
		\mathbf{y} = h(\mathbf{x},\mathbf{\mu},u)
		\end{align}
	\end{subequations}
	Identifiability concerns with the ability to determine a unique solution to the problem of estimating parameters $\mathbf{\mu}$ from given data on the system observables $\mathbf{y}$ for inputs $u$ \parencite{McLean2012}.	The identifiability of parameters in nonlinear models of physical processes can be classified into two categories: structural and practical identifiability.
